Kung Faux Pandas \\ \large Simplifying Privacy Protection

### 2018-06-01 paper/main.tex
Auto Update from local Sharelatex

\urlstyle{same}
\title{%
  Kung Faux Pandas \\
  \large Alternative Facts for Privacy Protection %Simplifying Privacy Protection?
  }

@@

% explain faux here? faux data - similar to faux fur or faux leather - ethically more appealing, less expensive to produce or use
This paper details an open source software library called \emph{Kung Faux Pandas (KFP)} which allows for the modular use of data security methods into the popular Python Pandas data science library. For those who prefer other tools, KFP also provides Structured Query Language (SQL) interface which enables users to arbitrarily query any data within a database, returning to the user a data set which either does not contain any personal information (synthesized) or has been anonymized by standard methods.

@@

Query pre-processor and synthesis process could optionally require a minimu source data size...

@@

% figure out how to adjust padding
\begin{wrapfigure}{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
  \centering
  \includegraphics[width=0.5\textwidth]{ui_screenshot3}
  \caption{User Interface.}
  \label{fig:ui}
\end{wrapfigure}
KFP provides multiple methods by which a machine learning developer can access on-demand synthetic data. Multiple methods of requesting and receiving faux data are provided. As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux data according to the selected synthesis method. Data can either be viewed directly in browser or downloaded in csv format for use in a machine learning process. Alternatively, an http REST service (utilized by the SPA) allows for cross language compatible requesting and receiving of faux data, again via SQL query. Lastly, for Python based software or languages with an interface to Python, the kungfauxpandas.py file and associated classes can be imported and called natively.

@@

Limitations, areas for further research:

\begin{itemize}
    \item Python module
    \item Currently don't impose any kind of result set minimum size
    \item Use in production
\end{itemize}

>>>>

\urlstyle{same}
\title{%
  Kung Faux Pandas \\
  \large Simplifying Privacy Protection
  }

@@

% explain faux here? faux data - similar to faux fur or faux leather - ethically more appealing, less expensive to produce or use
% faux data is a broader term that encompasses any data privacy protection method - synthesis, anonymization, grouping, perturbation, etc.
This paper details an open source software library called \emph{Kung Faux Pandas (KFP)} which allows for the modular use of data security methods into the popular Python Pandas data science library. For those who prefer other tools, KFP also provides Structured Query Language (SQL) interface which enables users to arbitrarily query any data within a database, returning to the user a data set which either does not contain any personal information (synthesized) or has been anonymized by standard methods.

@@

@@

% figure out how to adjust padding
\begin{wrapfigure}{r}{0.5\textwidth}%optionally place [15] after {wrapfigure} to control how many lines to wrap around figure
  \centering
  \includegraphics[width=0.5\textwidth]{ui_screenshot3}
  \caption{User Interface.}
  \label{fig:ui}
\end{wrapfigure}
KFP provides multiple methods by which a machine learning developer can access on-demand faux data. As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux data according to the selected generation method. Data can either be viewed directly in browser or downloaded in csv format for use in a machine learning process. Alternatively, an http REST service (utilized by the SPA) allows for cross language compatible requesting and receiving of faux data, again via SQL query. Lastly, for Python based software or languages with an interface to Python, the kungfauxpandas.py file and associated classes can be imported and called natively.

@@

Limitations, areas for further research - convert this to paragraph format:

\begin{itemize}
    \item Python module
    \item Currently don't impose any kind of result set minimum size. Query pre-processor and synthesis process could optionally require a minimum source data size to improve privacy protection...
    \item Use in production
\end{itemize}

### 2018-06-01 paper/seth.tex
Auto Update from local Sharelatex

 \section{Reproducibility}
 %Good discussion of what reproducibilty vs replicability means
 %http://languagelog.ldc.upenn.edu/nll/?p=21956
 Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability. Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result" \cite{leek_opinion_2015}; others such as Drummond use the terms in a reverse fashion \cite{drummond_replicability_2009}. Despite the semantic disagreement, both groups agree that an independent experiment with confirmatory results is the strongest support of any experiment. One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducbility as having: data, input parameters, documenation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by paper \cite{schwab_making_2000}. Reproducibility should be treated as a minimium required standard that all published research should meet \cite{peng_reproducible_2006}. Specifically in the context of machine learning, this means including details to a level someone else could create the same environment including hardware configuration and run times, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly. The last item is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article. Once a result can be reproduced, new researchers can then build upon the methods, gather new data for testing/validation, or discover alternative methods to replicate a result.

>>>>

 \section{Reproducibility}
 %Good discussion of what reproducibility vs replicability means
 %http://languagelog.ldc.upenn.edu/nll/?p=21956
 Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability. Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result" \cite{leek_opinion_2015}; others such as Drummond use the terms in a reverse fashion \cite{drummond_replicability_2009}. Despite the semantic disagreement, both groups agree that an independent experiment with confirmatory results is the strongest support of any experiment. One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducibility as having: data, input parameters, documentation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by paper \cite{schwab_making_2000}. Reproducibility should be treated as a minimum required standard that all published research should meet \cite{peng_reproducible_2006}. Specifically in the context of machine learning, this means including details to a level someone else could create the same environment including hardware configuration and run times, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly. The last item is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article. Once a result can be reproduced, new researchers can then build upon the methods, gather new data for testing/validation, or discover alternative methods to replicate a result.

 techniques for privacy protection:
 * De-identifcation
   * removal of known unique identifiers
   * Data summarization to prevent individual identification
 * Synthesis - Generating data based on some statistical model
